Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
intro added results

%% Although the technique has been intensively investigated in
%% research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
%% exception.

Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and Spectrum-Based Fault Localization
(\sfl{}) are two very popular techniques that leverage different principles
to automate fault isolation. An example of a MBSD is Dynamic
Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927},
a technique that traces back statements in the code that influence some
point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. Instead, it is a black-box, statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., methods) based on coverage information gathered
during the execution of test cases as well as the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
ranks the relevant parts of the code.

@@

The first question addresses the important problem of missing faulty
statements. Naturally, the consequence of that problem for debugging
is that developers would never be able to locate faults. Different
slicers can miss faulty statements for different reasons. In this
paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
which, in principle, could miss statements because of imprecise
oracles that guide the slicing process. We evaluated how often that
issue manifests in our experiments. The second research questions
effectively evaluates the impact of the combination. Our
results show that \Sof{@todo: sum up the results}.

>>>>

Model-based software diagnosis (MBSD)~\cite{REITER198757,DEKLEER200325} and
Spectrum-Based Fault Localization (\sfl{}) are two very popular techniques that
leverage different principles to automate fault isolation. An example of a MBSD
is Dynamic Slicing (DS)~\cite{Agrawal:1990:DPS:93542.93576} as well as some
work~\cite{wotawa2002model,Mayer:2008:EMM:1642931.1642950,mayer2008prioritising,Perez:2018:LQR:3304889.3304927,Ko:2008:DRA:1368088.1368130},
a technique that traces back statements in the code that influence some point of
interest, such as the evaluation of a failing assertion. In contrast to \ds{},
\sfl{}~\cite{7390282} does not analyze code. Instead, it is a black-box,
statistical fault localization method that computes suspiciousness values
associated with program entities (e.g., methods) based on coverage information
gathered during the execution of test cases as well as the output of test cases.
More precisely, \sfl{} uses coverage information of passing and failing test
cases to identify likely faulty statements and produces on output a list of
program entities ranked in decreasing order of suspiciousness. \ds{} and \sfl{}
are complementary debugging techniques~\cite{DBLP:conf/sac/AbreuGZG08}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{} ranks
the relevant parts of the code.

@@

The first question addresses the important problem of missing faulty
statements. Naturally, the consequence of that problem for debugging
is that developers would never be able to locate faults. Different
slicers can miss faulty statements for different reasons. In this
paper, we used Critical Slicing~\cite{DeMillo:1996:CSS:229000.226310},
which, in principle, could miss statements because of imprecise
oracles that guide the slicing process. We evaluated how often that
issue manifests in our experiments. The second research questions
effectively evaluates the impact of the combination. Our
results show that the combination of the two approaches improves the accuracy
of fault localization of 51\% of the studied faults.
